Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-12-08 metanalysis_visualization/visualization.Rmd
fixing pvalues and meta analysis

```{r}
outputDir <- "../../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

@@

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = quantile(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

annotation_function <- function(df, ...) {
  pvalue_coeff_interaction <- round(
    (1- max(
      sum(df[["periodduring_pandemic:time"]] > 0),
      sum(df[["periodduring_pandemic:time"]] < 0)
    )/nrow(df)) * 2
    , 3) 
  paste0("Coeffs differences: ",
                      round(mean(df[["periodduring_pandemic:time"]]), 2),
                      " (pvalue: ",
                      pvalue_coeff_interaction,
                      ")")
}

@@

```{r}
trend_model <- "percentage ~ period * time"
```

```{r}
trends_siteid <- meta_df %>% 
  filter((time_p >= as.Date("2019-02-01")) & (time_p <= as.Date("2021-05-01"))) %>% 
  filter(siteid != "APHP") %>% 
  group_by(siteid) %>% 
  group_modify( ~ broom::tidy(lm(as.formula(trend_model), data = .x))) %>%
  filter(term == c("periodduring_pandemic:time")) %>% 
  mutate(variance = std.error * std.error) %>% 
  select(siteid, estimate, variance)

model_meta_siteid <- metafor::rma(yi = estimate, 
             vi = variance,
             measure = "GEN",
             method = "DL",
  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
trends_country <- meta_df %>% 
  filter((time_p >= as.Date("2019-02-01")) & (time_p <= as.Date("2021-05-01"))) %>% 
  group_by(country) %>% 
  group_modify( ~ broom::tidy(lm(as.formula(trend_model), data = .x))) %>%
  filter(term == c("periodduring_pandemic:time")) %>% 
  mutate(variance = std.error * std.error) %>% 
  select(country, estimate, variance)

model_meta_country <- metafor::rma(yi = estimate, 
             vi = variance,
             measure = "GEN",
             method = "DL",
  data = trends_country) 
metafor::forest(model_meta_country,
                slab = trends_country$country,
                header="Sites",
                mlab="Overall temporal trend")
```

>>>>

```{r}
outputDir <- "../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

@@

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

annotation_function <- function(df, ...) {
  # pvalue_coeff_interaction <- round(
  #   (1- max(
  #     sum(df[["periodduring_pandemic:time"]] > 0),
  #     sum(df[["periodduring_pandemic:time"]] < 0)
  #   )/nrow(df)) * 2
  #   , 3)

  z <-  mean(df[["periodduring_pandemic:time"]]) / sd(df[["periodduring_pandemic:time"]])

  pvalue_coeff_interaction = round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(mean(df[["periodduring_pandemic:time"]]), 2),
         " (pvalue: ",
         pvalue_coeff_interaction,
         ")")
}

@@

```{r}
trends_siteid <- bootstrapped_coefficients_all %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

```{r}
# Fixed effects
model_meta_siteid <- metafor::rma(yi = mean_boot, 
             vi = var_boot,
             measure = "MN",
             method = "FE",
  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
# Random effects
model_meta_siteid <- metafor::rma(yi = mean_boot, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
trends_country <- bootstrapped_coefficients_all %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )

model_meta_country <- metafor::rma(yi = mean_boot, 
             vi = var_boot,
             measure = "MN",
             method = "FE",
  data = trends_country) 
metafor::forest(model_meta_country,
                slab = trends_country$country,
                header="Sites",
                mlab="Overall temporal trend")
```

### 2021-12-08 psy_peds_3.Rmd
dates correction
fixing pvalues and meta analysis

start_date_plots <- as.Date("2019-01-01")
end_date_plots <- as.Date("2021-05-24")

@@

bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list, .id = "iteration")
mean(bootstrapped_coefficients_df$time)
mean(bootstrapped_coefficients_df$time + bootstrapped_coefficients_df[["periodduring_pandemic:time"]])

pvalue_coeff_interaction <- round(
  (1- max(
    sum(bootstrapped_coefficients_df[["periodduring_pandemic:time"]] > 0),
        sum(bootstrapped_coefficients_df[["periodduring_pandemic:time"]] < 0)
  )/nrow(bootstrapped_coefficients_df)) * 2
  , 3)

>>>>

@@

bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration")

z <-  mean(bootstrapped_coefficients_df[["periodduring_pandemic:time"]]) / sd(bootstrapped_coefficients_df[["periodduring_pandemic:time"]])

pvalue_coeff_interaction <- round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
